A holomorphic approach to branes in twisted~$M$-theory

### 2022-08-22 fivebranes/fact.tex
end of day

\subsection{Summary}
\label{sec:factsummary}

We summarize the key points of this section.
In both the fivebrane and membrane case, we have described a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables restricted to the worldvolume of the fivebrane or membrane.
This factorization algebra is of the form 
\[
\pi_*\Obs_{sugra} = \clie^\bu(\cG)
\]
where $\cG$ is a sheaf of $L_\infty$ algebras on the worldvolume of the fivebrane or membrane.
While $\infty$ rank, $\cG$ is still well-behaved geometrically. 
It is given as the sheaf of sections of a pro vector bundle.

This local $L_\infty$ algebra came with a natural decomposition 
\[
\cG = \oplus_{j \geq -1} \cG^{(j)} .
\]
The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
This sequence of ideals induces a limit diagram of vector bundles
\beqn\label{eqn:lim}
0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
\eeqn
where $0$ is the zero vector bundle.
For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.

@@

The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
\beqn\label{eqn:colim}
\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
\eeqn
whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
Applying~$!$-duals we obtain a sequence
\beqn
\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
\eeqn 
whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
We also point out that there is a similar diagram of the form
\beqn\label{eqn:limit2}
\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
\eeqn

>>>>

\subsection{A finite $N$ conjecture}
\label{sec:factsummary}

We summarize the key points of this section which will lead to a general conjecture for the factorization algebra of observables for the worldvolume theory on a finite number of fivebranes in the holomorphic twist.
In the beginning of this section we defined a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables of twisted supergravity restricted to the worldvolume of the fivebrane or membrane.
This factorization algebra is of the form 
\[
\Bar{\pi}_*\Obs_{sugra} = \clie^\bu(\cG)
\]
where $\cG = \cG_Z$ is a sheaf of $L_\infty$ algebras on the worldvolume~$Z$ of the fivebrane.

We have seen that $\cG$ is given as the sheaf of sections of a pro vector bundle. 
In fact, the local $L_\infty$ algebra $\cG$ came with a natural decomposition 
\[
\cG = \oplus_{j \geq -1} \cG^{(j)} .
\]
The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
This sequence of ideals induces a limit diagram of vector bundles
\beqn\label{eqn:lim}
0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
\eeqn
where $0$ is the zero vector bundle.
For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.

@@

The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
\beqn\label{eqn:colim}
\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
\eeqn
whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
Applying~$!$-duals we obtain a sequence
\beqn\label{eqn:limit1}
\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
\eeqn 
whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
We also point out that there is a similar diagram of the form
\beqn\label{eqn:limit2}
\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
\eeqn 
whose limit is the universal factorization algebra of classical observables on the fivebrane 
\[
(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) .
\]

The first nonzero term in this limit diagram \eqref{eqn:limit1} is 
\[
\clie_\bu(\cG_{1,c})
\]
where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$. 
In \cite{SWtensor}, Saberi and the second author have given an explicit description of the holomorphic twist of the worldvolume theory on a single fivebrane, that is, the six-dimensional superconformal theory associated to the abelian Lie algebra~$\lie{gl}(1)$.
We denote the corresponding factorization algebra on the three-fold~$Z$ by~$\Obs_1$.

We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
This is a free theory and the underlying $\Z \times \Z/2$ graded cochain complex of fields $\cE_{1}$ with linear BRST differential is
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall in the $\Z \times \Z/2$ bigrading the differential has bidegree $(1,0)$. 
The factorization algebra $\Obs_1$ is given by~$\cO(\cE_1)$.

\begin{prop}
\label{prop:factabelian}
There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
\[
\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{1} .
\]
\end{prop}

\begin{proof}
In weight $(-1)$ the abelian local Lie algebra takes the form
\[
\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
\]
where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
\beqn\label{eqn:weight-1a}
\begin{tikzcd}
\ul{odd} & \ul{even}\\
\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
\end{tikzcd}
\eeqn
On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
\[
\cO(\cE_{1}(U)) = \Sym(\Pi \overline{\cE}_{1,c}^!(U)) .
\]
It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
The result then follows by applying ellipticity.
\end{proof}

We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.

We now formulate a general conjecture about the worldvolume theory on a stack of holomorphically twisted fivebranes.
Recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
In this form of the conjecture we focus only on the six-dimensional superconformal theories associated to Lie algebras of type $A$.

\begin{conj}
\label{conj:fact}
For $N > 1$, let $\Obs_N$ be the factorization algebra on $Z$ of classical observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$.
Then, there is an equivalence of factorization algebras on~$Z$:
\beqn
\Obs_{N} \simeq \clie_\bu(\cG_{N,c}) .
\eeqn 
\end{conj}
